---
title: "Untitled"
author: "JMH"
date: "3/18/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(kableExtra)
```

Load all models
```{r}
GPP_N_best <- read.csv(file.path(here::here("06_AICtables"), "03a_GPP_N.csv")) 
names(GPP_N_best) <- c("Int", "strTemp", "DOYresXstr", "light", "QresXstr", "dayTemp", "trt", "strTempXdayTemp",
                       "strTempXtrt", "DayTempXtrt", "strTempXDayTempXtrt", "Qres", "DOYresk5", "str", "DayTempXstr",
                       "trtXstr", "DayTempXtrtXstr", "df", "logLik", "AIC", "delta", "weight")

ER_N_best <- read.csv(file.path(here::here("06_AICtables"), "02a_ER_N.csv")) 
names(ER_N_best) <- c("Int", "strTemp", "DOYresXstr", "QresXstr", "dayTemp", "trt", "strTempXdayTemp",
                       "strTempXtrt", "DayTempXtrt", "strTempXDayTempXtrt", "Qres", "DOYresk5", "str", "DayTempXstr",
                       "trtXstr", "DayTempXtrtXstr", "df", "logLik", "AIC", "delta", "weight")

NEP_N_best <- read.csv(file.path(here::here("06_AICtables"), "03a_NEP_N.csv"))
names(NEP_N_best) <- c("Int", "strTemp", "DOYresXstr", "light", "QresXstr", "dayTemp", "trt", 
                       "strTempXtrt", "DayTempXtrt","Qres","strTempXdayTemp", "strTempXDayTempXtrt",  
                       "DOYresk5", "str", "DayTempXstr",
                       "trtXstr", "DayTempXtrtXstr", "df", "logLik", "AIC", "delta", "weight")


GPP_P_best <- read.csv(file.path(here::here("06_AICtables"), "03a_GPP_P.csv")) 
names(GPP_P_best) <- c("Int", "strTemp", 
                       "DOYresXstr",
                       "light", "QresXstr", "dayTemp", "trt", "strTempXdayTemp",
                       "strTempXtrt", "DayTempXtrt", "strTempXDayTempXtrt", 
                       "DOYresXstrM1",
                       "Qres", "DOYresk5", "str", "DayTempXstr",
                       "trtXstr", "DayTempXtrtXstr", "df", "logLik", "AIC", "delta", "weight")

ER_P_best <- read.csv(file.path(here::here("06_AICtables"), "02a_ER_P.csv")) 
names(ER_P_best) <- c("Int", "strTemp", "DOYresXstr", "QresXstr", "dayTemp", "trt", "strTempXdayTemp",
                       "strTempXtrt", "DayTempXtrt", "strTempXDayTempXtrt", "Qres", "DOYresK4", "str", "DayTempXstr",
                       "trtXstr", "DayTempXtrtXstr", "DOYresk5", "df", "logLik", "AIC", "delta", "weight")


NEP_P_best <- read.csv(file.path(here::here("06_AICtables"), "03a_NEP_P.csv")) 
names(NEP_P_best) <- c("Int", "strTemp", "DOYresXstrk4", "light", "QresXstr", "dayTemp", "trt", "strTempXdayTemp",
                       "strTempXtrt", "DayTempXtrt", "strTempXDayTempXtrt", "DOYresXstrk5", "Qres", "DOYresk5", "str",
                       "DayTempXstr",
                       "trtXstr", "DayTempXtrtXstr", "df", "logLik", "AIC", "delta", "weight")


GPP_AMB_best <- read.csv(file.path(here::here("06_AICtables"), "03d_GPP_AMB.csv")) 
names(GPP_AMB_best) <- c("Int", "strTemp", "DOYresXstr", "light", "QresXstr", "dayTemp", "strTempXdayTemp",
                        "Qres", "DOYresk5", "str", "DayTempXstr", "DOYresk4",
                        "df", "logLik", "AIC", "delta", "weight")

ER_AMB_best <- read.csv(file.path(here::here("06_AICtables"), "02d_ER_AMB.csv")) 
names(ER_AMB_best) <- c("Int", "strTemp", "DOYresXstr", "QresXstr", "dayTemp", "strTempXdayTemp",
                        "Qres", "DOYresk5", "str", "DayTempXstr",
                        "df", "logLik", "AIC", "delta", "weight")

NEP_AMB_best <- read.csv(file.path(here::here("06_AICtables"), "03d_NEP_AMB.csv")) 
names(NEP_AMB_best) <- c("Int", "strTemp", "DOYresXstr", "light", "QresXstr", "dayTemp", "strTempXdayTemp",
                        "Qres", "DOYresk5m1", "str", "DayTempXstr", "DOYresk5",
                        "df", "logLik", "AIC", "delta", "weight")
```



Cleaned AIC csv files
```{r}
write.csv(GPP_AMB_best, file.path(here::here("06_AICtables/CleanedFullAICtables"), "01_GPP_AMB.csv"))
write.csv(ER_AMB_best, file.path(here::here("06_AICtables/CleanedFullAICtables"), "01_ER_AMB.csv"))
write.csv(NEP_AMB_best, file.path(here::here("06_AICtables/CleanedFullAICtables"), "01_NEP_AMB.csv"))

write.csv(GPP_P_best, file.path(here::here("06_AICtables/CleanedFullAICtables"), "02_GPP_P.csv"))
write.csv(ER_P_best, file.path(here::here("06_AICtables/CleanedFullAICtables"), "02_ER_P.csv"))
write.csv(NEP_P_best, file.path(here::here("06_AICtables/CleanedFullAICtables"), "02_NEP_P.csv"))

write.csv(GPP_N_best, file.path(here::here("06_AICtables/CleanedFullAICtables"), "03_GPP_N.csv"))
write.csv(ER_N_best, file.path(here::here("06_AICtables/CleanedFullAICtables"), "03_ER_N.csv"))
write.csv(NEP_N_best, file.path(here::here("06_AICtables/CleanedFullAICtables"), "03_NEP_N.csv"))



```




NOTHING BELOW THIS UPDATED.......


























Function to make dataframe
  - Gets all models with delta AIC < 5
  - If models with delta AIC < 5 don't contain temp, then it grabs the top temp models and any within a delta AIC of 2.
Function for GPP and NEP, in treatments
```{r}
ModelTabFun_gppNEP_trt <- function(model.tab){
  # model.tab <- GPP_N_best
  model.tab.d5 <- model.tab %>% 
  filter(delta < 5)

TempInTopD5 <- max(ifelse(is.na(model.tab.d5$strTemp) == TRUE,1,0)) #if true 1 other 0 

model.tab.Temp <- if(TempInTopD5 > 0) {
  model.tab.TempPend <- model.tab %>% 
    # get all of the models with stream temp
    filter(!is.na(model.tab$strTemp)) %>% 
    # calculate a new deltaAIC
    mutate(delta2 = AIC - min(AIC)) %>% 
    # get models with deltaAIC <2
    filter(delta2 < 2) %>% 
    select(-delta2)
  
  model.tab.final <-  rbind(model.tab.d5, model.tab.TempPend) %>% 
  mutate(model = paste0(
    ifelse(!is.na(strTempXDayTempXtrt),"strTemp X DayTemp X trt + ",
      ifelse(is.na(strTempXDayTempXtrt) & !is.na(strTempXtrt) & !is.na(DayTempXtrt),"strTemp X trt + DayTemp X trt + ",
        ifelse(is.na(strTempXDayTempXtrt) & !is.na(strTempXtrt) & is.na(DayTempXtrt), "strTemp X trt + ",
          ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & !is.na(DayTempXtrt) & is.na(DayTempXtrtXstr),"DayTemp X trt + ",
            ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & is.na(DayTempXtrt) & is.na(DayTempXtrtXstr) & !is.na(trt),
                   "trt + ", ""))))),
    ifelse(!is.na(DayTempXtrtXstr),"DayTemp X trt X str + ",
           ifelse(is.na(DayTempXtrtXstr) & !is.na(DayTempXstr) & !is.na(trtXstr),"DayTemp X str + trt X str + ",
              ifelse(is.na(DayTempXtrtXstr) & !is.na(DayTempXstr) & is.na(trtXstr), "strTemp X trt + ",
                ifelse(is.na(strTempXDayTempXtrt) & is.na(DayTempXtrtXstr) & !is.na(DayTempXtrt) & is.na(trtXstr),"DayTemp X trt + ",
                  ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & is.na(DayTempXtrt) & is.na(DayTempXtrtXstr) & !is.na(trt),
                   "trt + ", ""))))),
    ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & is.na(DayTempXtrt) & !is.na(strTemp),"strTemp + ",""),
    ifelse(is.na(DayTempXtrtXstr) & is.na(DayTempXstr) & is.na(strTempXDayTempXtrt) & is.na(DayTempXtrt) & !is.na(dayTemp),"dayTemp + ",""),
    ifelse(!is.na(DOYresXstr),"DOYres X str + ",""),
    ifelse(!is.na(QresXstr),"Qres X str + ",""),
    ifelse(!is.na(DOYres),"DOYres + ",""),
    ifelse(!is.na(light), "L + ",""),
    ifelse(!is.na(Qres),"Qres", ""))) %>% 
  select(model, df, AIC, delta)
  
} else {
  
  model.tab.final <-  model.tab.d5 %>% 
  mutate(model = paste0(
    ifelse(!is.na(strTempXDayTempXtrt),"strTemp X DayTemp X trt + ",
      ifelse(is.na(strTempXDayTempXtrt) & !is.na(strTempXtrt) & !is.na(DayTempXtrt),"strTemp X trt + DayTemp X trt + ",
        ifelse(is.na(strTempXDayTempXtrt) & !is.na(strTempXtrt) & is.na(DayTempXtrt), "strTemp X trt + ",
          ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & !is.na(DayTempXtrt) & is.na(DayTempXtrtXstr),"DayTemp X trt + ",
            ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & is.na(DayTempXtrt) & is.na(DayTempXtrtXstr) & !is.na(trt),
                   "trt + ", ""))))),
    ifelse(!is.na(DayTempXtrtXstr),"DayTemp X trt X str + ",
           ifelse(is.na(DayTempXtrtXstr) & !is.na(DayTempXstr) & !is.na(trtXstr),"DayTemp X str + trt X str + ",
              ifelse(is.na(DayTempXtrtXstr) & !is.na(DayTempXstr) & is.na(trtXstr), "strTemp X trt + ",
                ifelse(is.na(strTempXDayTempXtrt) & is.na(DayTempXtrtXstr) & !is.na(DayTempXtrt) & is.na(trtXstr),"DayTemp X trt + ",
                  ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & is.na(DayTempXtrt) & is.na(DayTempXtrtXstr) & !is.na(trt),
                   "trt + ", ""))))),
    ifelse(is.na(DayTempXtrtXstr) & is.na(DayTempXstr) & is.na(trtXstr) & !is.na(trt),"trt + ",""),
    ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & is.na(DayTempXtrt) & !is.na(strTemp),"strTemp + ",""),
    ifelse(is.na(DayTempXtrtXstr) & is.na(DayTempXstr) & is.na(strTempXDayTempXtrt) & is.na(DayTempXtrt) & !is.na(dayTemp),"dayTemp + ",""),
    ifelse(!is.na(DOYresXstr),"DOYres X str + ",""),
    ifelse(!is.na(QresXstr),"Qres X str + ",""),
    ifelse(!is.na(DOYres),"DOYres + ",""),
    ifelse(!is.na(light), "L + ",""),
    ifelse(!is.na(Qres),"Qres", ""))) %>% 
  select(model, df, AIC, delta)
}



model.tab.final

}

```

This is function for ER, since missing light, in treatments
```{r}
ModelTabFun_ER_trt <- function(model.tab){
  # model.tab <- ER_N_best
  model.tab.d5 <- model.tab %>% 
  filter(delta < 5)

TempInTopD5 <- max(ifelse(is.na(model.tab.d5$strTemp) == TRUE,1,0)) #if true 1 other 0 

model.tab.Temp <- if(TempInTopD5 > 0) {
  model.tab.TempPend <- model.tab %>% 
    # get all of the models with stream temp
    filter(!is.na(model.tab$strTemp)) %>% 
    # calculate a new deltaAIC
    mutate(delta2 = AIC - min(AIC)) %>% 
    # get models with deltaAIC <2
    filter(delta2 < 2) %>% 
    select(-delta2)
  
  model.tab.final <-  rbind(model.tab.d5, model.tab.TempPend) %>% 
  mutate(model = paste0(
     ifelse(!is.na(strTempXDayTempXtrt),"strTemp X DayTemp X trt + ",
      ifelse(is.na(strTempXDayTempXtrt) & !is.na(strTempXtrt) & !is.na(DayTempXtrt),"strTemp X trt + DayTemp X trt + ",
        ifelse(is.na(strTempXDayTempXtrt) & !is.na(strTempXtrt) & is.na(DayTempXtrt), "strTemp X trt + ",
          ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & !is.na(DayTempXtrt) & is.na(DayTempXtrtXstr),"DayTemp X trt + ",
            ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & is.na(DayTempXtrt) & is.na(DayTempXtrtXstr) & !is.na(trt),
                   "trt + ", ""))))),
    ifelse(!is.na(DayTempXtrtXstr),"DayTemp X trt X str + ",
           ifelse(is.na(DayTempXtrtXstr) & !is.na(DayTempXstr) & !is.na(trtXstr),"DayTemp X str + trt X str + ",
              ifelse(is.na(DayTempXtrtXstr) & !is.na(DayTempXstr) & is.na(trtXstr), "strTemp X trt + ",
                ifelse(is.na(strTempXDayTempXtrt) & is.na(DayTempXtrtXstr) & !is.na(DayTempXtrt) & is.na(trtXstr),"DayTemp X trt + ",
                  ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & is.na(DayTempXtrt) & is.na(DayTempXtrtXstr) & !is.na(trt),
                   "trt + ", ""))))),
    ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & is.na(DayTempXtrt) & !is.na(strTemp),"strTemp + ",""),
    ifelse(is.na(DayTempXtrtXstr) & is.na(DayTempXstr) & is.na(strTempXDayTempXtrt) & is.na(DayTempXtrt) & !is.na(dayTemp),"dayTemp + ",""),
    ifelse(!is.na(DOYresXstr),"DOYres X str + ",""),
    ifelse(!is.na(QresXstr),"Qres X str + ",""),
    ifelse(!is.na(DOYres),"DOYres + ",""),
    ifelse(!is.na(Qres),"Qres", ""))) %>% 
  select(model, df, AIC, delta)
  
} else {
  
  model.tab.final <-  model.tab.d5 %>% 
  mutate(model = paste0(
     ifelse(!is.na(strTempXDayTempXtrt),"strTemp X DayTemp X trt + ",
      ifelse(is.na(strTempXDayTempXtrt) & !is.na(strTempXtrt) & !is.na(DayTempXtrt),"strTemp X trt + DayTemp X trt + ",
        ifelse(is.na(strTempXDayTempXtrt) & !is.na(strTempXtrt) & is.na(DayTempXtrt), "strTemp X trt + ",
          ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & !is.na(DayTempXtrt) & is.na(DayTempXtrtXstr),"DayTemp X trt + ",
            ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & is.na(DayTempXtrt) & is.na(DayTempXtrtXstr) & !is.na(trt),
                   "trt + ", ""))))),
    ifelse(!is.na(DayTempXtrtXstr),"DayTemp X trt X str + ",
           ifelse(is.na(DayTempXtrtXstr) & !is.na(DayTempXstr) & !is.na(trtXstr),"DayTemp X str + trt X str + ",
              ifelse(is.na(DayTempXtrtXstr) & !is.na(DayTempXstr) & is.na(trtXstr), "strTemp X trt + ",
                ifelse(is.na(strTempXDayTempXtrt) & is.na(DayTempXtrtXstr) & !is.na(DayTempXtrt) & is.na(trtXstr),"DayTemp X trt + ",
                  ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & is.na(DayTempXtrt) & is.na(DayTempXtrtXstr) & !is.na(trt),
                   "trt + ", ""))))),
    ifelse(is.na(strTempXDayTempXtrt) & is.na(strTempXtrt) & is.na(DayTempXtrt) & !is.na(strTemp),"strTemp + ",""),
    ifelse(is.na(DayTempXtrtXstr) & is.na(DayTempXstr) & is.na(strTempXDayTempXtrt) & is.na(DayTempXtrt) & !is.na(dayTemp),"dayTemp + ",""),
    ifelse(!is.na(DOYresXstr),"DOYres X str + ",""),
    ifelse(!is.na(QresXstr),"Qres X str + ",""),
    ifelse(!is.na(DOYres),"DOYres + ",""),
    ifelse(!is.na(Qres),"Qres", ""))) %>% 
  select(model, df, AIC, delta)
}



model.tab.final

}

```

Function for GPP and NEP in amb
```{r}
ModelTabFun_gppNEP_amb <- function(model.tab){
  # model.tab <- GPP_AMB_best
  model.tab.d5 <- model.tab %>% 
  filter(delta < 5)

TempInTopD5 <- max(ifelse(is.na(model.tab.d5$strTemp) == TRUE,1,0)) #if true 1 other 0 

model.tab.Temp <- if(TempInTopD5 > 0) {
  model.tab.TempPend <- model.tab %>% 
    # get all of the models with stream temp
    filter(!is.na(model.tab$strTemp)) %>% 
    # calculate a new deltaAIC
    mutate(delta2 = AIC - min(AIC)) %>% 
    # get models with deltaAIC <2
    filter(delta2 < 2) %>% 
    select(-delta2)
  
  model.tab.final <-  rbind(model.tab.d5, model.tab.TempPend) %>% 
  mutate(model = paste0(
    ifelse(!is.na(strTempXdayTemp), "strTemp X DayTemp + ",
           ifelse(is.na(strTempXdayTemp) & !is.na(strTemp) & !is.na(dayTemp), "strTemp + dayTemp + ",
                  ifelse(is.na(strTempXdayTemp) & !is.na(strTemp) & is.na(dayTemp), "strTemp + ",
                         ifelse(is.na(strTempXdayTemp) & is.na(strTemp) & !is.na(dayTemp), "dayTemp + ","")))),
    ifelse(!is.na(DOYresXstr),"DOYres X str + ",""),
    ifelse(!is.na(QresXstr),"Qres X str + ",""),
    ifelse(!is.na(DOYres),"DOYres + ",""),
    ifelse(!is.na(light), "L + ",""),
    ifelse(!is.na(Qres),"Qres", ""))) %>% 
  select(model, df, AIC, delta)
  
} else {
  
  model.tab.final <-  model.tab.d5 %>% 
  mutate(model = paste0(
    ifelse(!is.na(strTempXdayTemp), "strTemp X DayTemp + ",
           ifelse(is.na(strTempXdayTemp) & !is.na(strTemp) & !is.na(dayTemp), "strTemp + dayTemp + ",
                  ifelse(is.na(strTempXdayTemp) & !is.na(strTemp) & is.na(dayTemp), "strTemp + ",
                         ifelse(is.na(strTempXdayTemp) & is.na(strTemp) & !is.na(dayTemp), "dayTemp + ","")))),
    ifelse(!is.na(DOYresXstr),"DOYres X str + ",""),
    ifelse(!is.na(QresXstr),"Qres X str + ",""),
    ifelse(!is.na(DOYres),"DOYres + ",""),
    ifelse(!is.na(light), "L + ",""),
    ifelse(!is.na(Qres),"Qres", ""))) %>% 
  select(model, df, AIC, delta)
}



model.tab.final

}

```




```{r}
ModelTabFun_ER_amb <- function(model.tab){
  # model.tab <- ER_N_best
  model.tab.d5 <- model.tab %>% 
  filter(delta < 5)

TempInTopD5 <- max(ifelse(is.na(model.tab.d5$strTemp) == TRUE,1,0)) #if true 1 other 0 

model.tab.Temp <- if(TempInTopD5 > 0) {
  model.tab.TempPend <- model.tab %>% 
    # get all of the models with stream temp
    filter(!is.na(model.tab$strTemp)) %>% 
    # calculate a new deltaAIC
    mutate(delta2 = AIC - min(AIC)) %>% 
    # get models with deltaAIC <2
    filter(delta2 < 2) %>% 
    select(-delta2)
  
  model.tab.final <-  rbind(model.tab.d5, model.tab.TempPend) %>% 
 mutate(model = paste0(
    ifelse(!is.na(strTempXdayTemp), "strTemp X DayTemp + ",
           ifelse(is.na(strTempXdayTemp) & !is.na(strTemp) & !is.na(dayTemp), "strTemp + dayTemp + ",
                  ifelse(is.na(strTempXdayTemp) & !is.na(strTemp) & is.na(dayTemp), "strTemp + ",
                         ifelse(is.na(strTempXdayTemp) & is.na(strTemp) & !is.na(dayTemp), "dayTemp + ","")))),
    ifelse(!is.na(DOYresXstr),"DOYres X str + ",""),
    ifelse(!is.na(QresXstr),"Qres X str + ",""),
    ifelse(!is.na(DOYres),"DOYres + ",""),
    ifelse(!is.na(Qres),"Qres", ""))) %>% 
  select(model, df, AIC, delta)
  
} else {
  
  model.tab.final <-  model.tab.d5 %>% 
 mutate(model = paste0(
    ifelse(!is.na(strTempXdayTemp), "strTemp X DayTemp + ",
           ifelse(is.na(strTempXdayTemp) & !is.na(strTemp) & !is.na(dayTemp), "strTemp + dayTemp + ",
                  ifelse(is.na(strTempXdayTemp) & !is.na(strTemp) & is.na(dayTemp), "strTemp + ",
                         ifelse(is.na(strTempXdayTemp) & is.na(strTemp) & !is.na(dayTemp), "dayTemp + ","")))),
    ifelse(!is.na(DOYresXstr),"DOYres X str + ",""),
    ifelse(!is.na(QresXstr),"Qres X str + ",""),
    ifelse(!is.na(DOYres),"DOYres + ",""),
    ifelse(!is.na(Qres),"Qres", ""))) %>% 
  select(model, df, AIC, delta)
}



model.tab.final

}

```

```{r}
GPP_N_best.mt <- ModelTabFun_gppNEP_trt(GPP_N_best)
ER_N_best.mt <- ModelTabFun_ER_trt(ER_N_best)
NEP_N_best.mt <- ModelTabFun_gppNEP_trt(NEP_N_best)

GPP_P_best.mt <- ModelTabFun_gppNEP_trt(GPP_P_best)
ER_P_best.mt <- ModelTabFun_ER_trt(ER_P_best)
NEP_P_best.mt <- ModelTabFun_gppNEP_trt(NEP_P_best)

GPP_AMB_best.mt <- ModelTabFun_gppNEP_amb(GPP_AMB_best)
ER_AMB_best.mt <- ModelTabFun_ER_amb(ER_AMB_best)
NEP_AMB_best.mt <- ModelTabFun_gppNEP_amb(NEP_AMB_best)
```


```{r}
AllMods <- rbind(GPP_N_best.mt %>% 
                   mutate(trt = "N",
                          met = "GPP"),
                 ER_N_best.mt %>% 
                   mutate(trt = "N",
                          met = "ER"),
                 NEP_N_best.mt %>% 
                   mutate(trt = "N",
                          met = "NEP"),
                 GPP_P_best.mt %>% 
                   mutate(trt = "P",
                          met = "GPP"),
                 ER_P_best.mt %>% 
                   mutate(trt = "P",
                          met = "ER"),
                 NEP_P_best.mt %>% 
                   mutate(trt = "P",
                          met = "NEP"),
                 GPP_AMB_best.mt %>% 
                   mutate(trt = "AMB",
                          met = "GPP"),
                 ER_AMB_best.mt %>% 
                   mutate(trt = "AMB",
                          met = "ER"),
                 NEP_AMB_best.mt %>% 
                   mutate(trt = "AMB",
                          met = "NEP")) %>% 
  select(trt, met, model, df, AIC, delta)
```


```{r}
write_csv(AllMods,
          file.path(here::here("06_AICtables"), "00_allAICtables.csv"))
```



```{r}
GPP_N_best.mt %>% 
  kable() %>% 
  kable_styling()
```


```{r}
ER_N_best.mt %>% 
  kable() %>% 
  kable_styling()
```


```{r}
NEP_N_best.mt %>% 
  kable() %>% 
  kable_styling()
```


```{r}
GPP_P_best.mt %>% 
  kable() %>% 
  kable_styling()
```


```{r}
ER_P_best.mt %>% 
  kable() %>% 
  kable_styling()
```

```{r}
GPP_AMB_best.mt %>% 
  kable() %>% 
  kable_styling()
```


```{r}
ER_AMB_best.mt %>% 
  kable() %>% 
  kable_styling()
```


```{r}
NEP_AMB_best.mt %>% 
  kable() %>% 
  kable_styling()
```

